Security Metrics for the Android Ecosystem

### 2015-07-23 dastats.tex
./update.sh

\newcommand{\daNumSigModels}{17}

@@

\newcommand{\daOSYearsOfData}{3}
\newcommand{\daOSMonthsOfData}{47}

@@

\newcommand{\daEndDate}{2015-05-31}

@@

\newcommand{\daNumManufacturers}{299}
\newcommand{\daNumSigManufacturers}{8}
\newcommand{\daNumModels}{2\,700}
\newcommand{\daNumOperators}{1\,440}

@@

\newcommand{\daNumOSDevices}{20\,300}
\newcommand{\daOSVersionPercValidLines}{99.7\%}
\newcommand{\daOSTotalDaysData}{1\,290\,000}
\newcommand{\daMeanInsecurityPercNominal}{87.9\%}
\newcommand{\daMeanInsecurityPerc}{$87.9 \pm 0.0\%$}

@@

\newcommand{\daMeanSecurityPercNominal}{12.1\%}
\newcommand{\daMeanSecurityPerc}{$12.1 \pm 0.0\%$}

@@

\newcommand{\daVulnFreeNominal}{0.121}
\newcommand{\daVulnFree}{$0.121 \pm 0.000$}
\newcommand{\daMeanOutstandingVulnerabilities}{$0.547 \pm 2.45e$}
\newcommand{\daUpdatednessNominal}{0.0511}
\newcommand{\daUpdatedness}{$0.0511 \pm 0.0002$}
\newcommand{\daUpdatednessPercNominal}{5.11\%}
\newcommand{\daUpdatednessPerc}{$5.11 \pm 0.02\%$}
\newcommand{\daUpdatednessPercTwosfNominal}{5.1\%}
\newcommand{\daUpdatednessPercTwosf}{$5.1 \pm 0.0\%$}
\newcommand{\daSecurityScoreNominal}{2.84}
\newcommand{\daSecurityScore}{$2.84 \pm 0.00$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{85.4\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$85.4 \pm 0.1\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{85\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$85 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{14.6\%}
\newcommand{\daCurrentMeanSecurityPerc}{$14.6 \pm 0.1\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{15\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$15 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.146}
\newcommand{\daCurrentVulnFree}{$0.146 \pm 0.001$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.193 \pm 1.11e$}
\newcommand{\daCurrentUpdatednessNominal}{0.0326}
\newcommand{\daCurrentUpdatedness}{$0.0326 \pm 0.0006$}
\newcommand{\daCurrentUpdatednessPercNominal}{3.26\%}
\newcommand{\daCurrentUpdatednessPerc}{$3.26 \pm 0.06\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{3.3\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$3.3 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{3.39}
\newcommand{\daCurrentSecurityScore}{$3.39 \pm 0.00$}
\newcommand{\daDailyParticipationNominal}{903}
\newcommand{\daDailyParticipation}{$903 \pm 227$}
\newcommand{\daNumFullVersions}{1\,250}
\newcommand{\daNumSigFullVersions}{94}

@@

\newcommand{\daNumSigOSVersions}{27}

@@

\newcommand{\daNumFullVersionUpdates}{4\,540}
\newcommand{\daNumOSVersionUpdates}{3\,850}
\newcommand{\daUpdatesPerYearNominal}{1.28}
\newcommand{\daUpdatesPerYear}{$1.28 \pm 0.01$}

@@

\newcommand{\daNumFullOnlyVersionUpdates}{673}
\newcommand{\daNumSecurityUpdates}{1\,240}
\newcommand{\daNumPossibleSecurityUpdates}{2\,290}
\newcommand{\daOSCurveFitParamFirst}{84.8}
\newcommand{\daOSCurveFitParamSecond}{\num{0.00289}}
\newcommand{\daOSCurveFitRMSE}{0.116}
\newcommand{\daOSCurvePolyRMSE}{0.116}
\newcommand{\daOSCurveSplineRMSE}{0.116}
\newcommand{\daOSCurveHalfDeployedYearsNominal}{0.888}
\newcommand{\daOSCurveHalfDeployedYears}{$0.888 \pm 0.249$}
\newcommand{\daOSCurveHalfDeployedNominal}{324}
\newcommand{\daOSCurveHalfDeployed}{$324 \pm 90$}
\newcommand{\daOSCurveFullDeployedYearsNominal}{3.07}
\newcommand{\daOSCurveFullDeployedYears}{$3.07 \pm 70$}
\newcommand{\daOSCurveFullDeployedNominal}{1\,120}
\newcommand{\daOSCurveFullDeployed}{$1\,120 \pm 256\,000$}
\newcommand{\daAPICurveFitParamFirst}{102}
\newcommand{\daAPICurveFitParamSecond}{\num{0.00289}}
\newcommand{\daAPICurveFitRMSE}{0.113}
\newcommand{\daAPICurvePolyRMSE}{0.113}
\newcommand{\daAPICurveSplineRMSE}{0.113}
\newcommand{\daAPICurveHalfDeployedYearsNominal}{0.934}
\newcommand{\daAPICurveHalfDeployedYears}{$0.934 \pm 0.243$}
\newcommand{\daAPICurveHalfDeployedNominal}{341}
\newcommand{\daAPICurveHalfDeployed}{$341 \pm 88$}
\newcommand{\daAPICurveFullDeployedYearsNominal}{3.11}
\newcommand{\daAPICurveFullDeployedYears}{$3.11 \pm 70$}
\newcommand{\daAPICurveFullDeployedNominal}{1\,140}
\newcommand{\daAPICurveFullDeployed}{$1\,140 \pm 256\,000$}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.20 \pm 0.00$ & $0.33 \pm 0.00$ & $0.63 \pm 0.01$ & $3.86 \pm 0.02$ \\  Motorola & $0.18 \pm 0.00$ & $0.13 \pm 0.00$ & $0.73 \pm 0.02$ & $3.03 \pm 0.02$ \\  Samsung & $0.13 \pm 0.00$ & $0.04 \pm 0.00$ & $0.63 \pm 0.00$ & $2.72 \pm 0.00$ \\  Sony & $0.13 \pm 0.00$ & $0.19 \pm 0.00$ & $1.09 \pm 0.02$ & $2.61 \pm 0.02$ \\  HTC & $0.14 \pm 0.00$ & $0.09 \pm 0.00$ & $0.89 \pm 0.01$ & $2.58 \pm 0.02$ \\  asus & $0.19 \pm 0.00$ & $0.52 \pm 0.01$ & $6.01 \pm 0.07$ & $2.32 \pm 0.02$ \\  other & $0.06 \pm 0.00$ & $0.04 \pm 0.00$ & $1.03 \pm 0.01$ & $1.95 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $5.00 \pm 0.05$ & $0.28 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $5.96 \pm 0.08$ & $0.25 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table*}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{3.86}
\newcommand{\daSecScoreBestmanufacturerScore}{$3.86 \pm 0.02$}
\newcommand{\daSecScoreBestmanufacturerNumFullVersions}{131}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.251}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.251 \pm 0.007$}
\newcommand{\daSecScoreWorstmanufacturerNumFullVersions}{22}
\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.51 \pm 0.00$ & $0.55 \pm 0.01$ & $1.53 \pm 0.04$ & $4.74 \pm 0.04$ \\  Nexus 4 & $0.28 \pm 0.00$ & $0.82 \pm 0.01$ & $6.06 \pm 0.09$ & $3.61 \pm 0.04$ \\  Nexus 7 & $0.24 \pm 0.00$ & $0.74 \pm 0.01$ & $5.92 \pm 0.09$ & $3.19 \pm 0.04$ \\  other & $0.09 \pm 0.00$ & $0.14 \pm 0.00$ & $0.55 \pm 0.00$ & $2.98 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & $0.39 \pm 0.02$ & $2.91 \pm 0.04$ \\  HTC Sensation & $0.34 \pm 0.00$ & $0.01 \pm 0.01$ & $1.59 \pm 0.05$ & $2.41 \pm 0.05$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & $1.23 \pm 0.02$ & $2.28 \pm 0.02$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.06$ & $1.75 \pm 0.07$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $2.52 \pm 0.05$ & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $1.79 \pm 0.06$ & $0.90 \pm 0.05$ \\  GT-I9300 & $0.13 \pm 0.00$ & $0.01 \pm 0.00$ & $6.25 \pm 0.04$ & $0.58 \pm 0.01$ \\  GT-I9505 & $0.01 \pm 0.00$ & $0.13 \pm 0.00$ & $6.83 \pm 0.07$ & $0.46 \pm 0.01$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $3.05 \pm 0.05$ & $0.27 \pm 0.03$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & $6.91 \pm 0.08$ & $0.25 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $11.00 \pm 0.12$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}

@@

\newcommand{\daSecScoreBestmodelScoreNominal}{4.74}
\newcommand{\daSecScoreBestmodelScore}{$4.74 \pm 0.04$}

@@

\newcommand{\daSecScoreWorstmodelScore}{$0.0001 \pm 0.0275$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline nexus & $0.38 \pm 0.00$ & $0.47 \pm 0.00$ & $0.58 \pm 0.01$ & $5.07 \pm 0.02$ \\  notnexus & $0.10 \pm 0.00$ & $0.02 \pm 0.00$ & $0.55 \pm 0.00$ & $2.67 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table*}}
\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.26 \pm 0.00$ & $0.12 \pm 0.00$ & $0.37 \pm 0.02$ & $3.85 \pm 0.03$ \\  T-Mobile & $0.21 \pm 0.00$ & $0.18 \pm 0.00$ & $0.42 \pm 0.02$ & $3.73 \pm 0.03$ \\  Orange & $0.21 \pm 0.00$ & $0.09 \pm 0.00$ & $0.39 \pm 0.03$ & $3.52 \pm 0.04$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & $0.40 \pm 0.02$ & $3.46 \pm 0.03$ \\  3 & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & $0.52 \pm 0.03$ & $3.24 \pm 0.04$ \\  Vodafone uk & $0.13 \pm 0.00$ & $0.13 \pm 0.00$ & $0.50 \pm 0.03$ & $3.18 \pm 0.04$ \\  AT\&T & $0.13 \pm 0.00$ & $0.08 \pm 0.00$ & $0.43 \pm 0.02$ & $3.10 \pm 0.02$ \\  Verizon & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & $0.82 \pm 0.02$ & $2.83 \pm 0.02$ \\  unknown & $0.11 \pm 0.00$ & $0.20 \pm 0.00$ & $0.86 \pm 0.02$ & $2.81 \pm 0.02$ \\  n Telenor & $0.03 \pm 0.00$ & $0.12 \pm 0.00$ & $1.25 \pm 0.02$ & $1.82 \pm 0.02$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & $1.62 \pm 0.03$ & $1.28 \pm 0.03$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $2.08 \pm 0.04$ & $0.90 \pm 0.03$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.02 \pm 0.02$ & $0.85 \pm 0.01$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.60 \pm 0.04$ & $0.54 \pm 0.02$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}

@@

\newcommand{\daSecScoreBestoperatorScoreNominal}{3.85}
\newcommand{\daSecScoreBestoperatorScore}{$3.85 \pm 0.02$}
\newcommand{\daSecScoreBestoperatorNumFullVersions}{96}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.545}
\newcommand{\daSecScoreWorstoperatorScore}{$0.545 \pm 0.018$}

@@

\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline equal & 0.0 & 0.0 & 0.0714 & 0.0 \\weight $m$ & 0.222 & 0.333 & 0.143 & 0.0 \\weight $u$ & 0.444 & 0.133 & 0.214 & 0.0 \\$f$ & 0.444 & 0.733 & 0.5 & 0.0 \\$m$ & 0.667 & 0.733 & 0.357 & 0.5 \\$u$ & 0.778 & 0.733 & 0.714 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline $m$ & $-1.9 \pm 2.2$ & $-0.664 \pm 2.51$ & $-3.27 \pm 1.39$ & $-3.38 \pm 1.83$ \\weight $m$ & $-0.294 \pm 0.275$ & $-0.101 \pm 0.316$ & $-0.458 \pm 0.177$ & $-0.487 \pm 0.209$ \\equal & $-0.116 \pm 0.064$ & $-0.0386 \pm 0.113$ & $-0.146 \pm 0.048$ & $-0.166 \pm 0.029$ \\weight $u$ & $-0.0522 \pm 0.126$ & $-0.0148 \pm 0.238$ & $0.0206 \pm 0.0797$ & $-0.00995 \pm 0.123$ \\$u$ & $0.517 \pm 1.61$ & $0.2 \pm 2.1$ & $1.52 \pm 0.96$ & $1.39 \pm 1.48$ \\$f$ & $1.04 \pm 0.58$ & $0.348 \pm 1.01$ & $1.31 \pm 0.43$ & $1.49 \pm 0.26$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}
\newcommand{\daGPAPICurveFitParamFirst}{80.7}
\newcommand{\daGPAPICurveFitParamSecond}{\num{0.00259}}
\newcommand{\daGPAPICurveFitRMSE}{0.18}
\newcommand{\daGPAPICurvePolyRMSE}{0.18}
\newcommand{\daGPAPICurveSplineRMSE}{0.18}
\newcommand{\daGPAPICurveHalfDeployedYearsNominal}{0.953}
\newcommand{\daGPAPICurveHalfDeployedYears}{$0.953 \pm 0.472$}
\newcommand{\daGPAPICurveHalfDeployedNominal}{348}
\newcommand{\daGPAPICurveHalfDeployed}{$348 \pm 172$}
\newcommand{\daGPAPICurveFullDeployedYearsNominal}{3.39}

>>>>

\newcommand{\daNumSigModels}{18}

@@

\newcommand{\daOSYearsOfData}{4}
\newcommand{\daOSMonthsOfData}{49}

@@

\newcommand{\daEndDate}{2015-07-14}

@@

\newcommand{\daNumManufacturers}{300}
\newcommand{\daNumSigManufacturers}{10}
\newcommand{\daNumModels}{2\,730}
\newcommand{\daNumOperators}{1\,460}

@@

\newcommand{\daNumOSDevices}{20\,400}
\newcommand{\daOSVersionPercValidLines}{99.9\%}
\newcommand{\daOSTotalDaysData}{1\,330\,000}
\newcommand{\daMeanInsecurityPercNominal}{87.7\%}
\newcommand{\daMeanInsecurityPerc}{$87.7 \pm 0.0\%$}

@@

\newcommand{\daMeanSecurityPercNominal}{12.3\%}
\newcommand{\daMeanSecurityPerc}{$12.3 \pm 0.0\%$}

@@

\newcommand{\daVulnFreeNominal}{0.123}
\newcommand{\daVulnFree}{$0.123 \pm 0.0$}
\newcommand{\daMeanOutstandingVulnerabilities}{$0.531 \pm 0.0$}
\newcommand{\daUpdatednessNominal}{0.0521}
\newcommand{\daUpdatedness}{$0.0521 \pm 0.0$}
\newcommand{\daUpdatednessPercNominal}{5.21\%}
\newcommand{\daUpdatednessPerc}{$5.21 \pm 0.0\%$}
\newcommand{\daUpdatednessPercTwosfNominal}{5.2\%}
\newcommand{\daUpdatednessPercTwosf}{$5.2 \pm 0.0\%$}
\newcommand{\daSecurityScoreNominal}{2.87}
\newcommand{\daSecurityScore}{$2.87 \pm 0.0$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{79.7\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$79.7 \pm 0.0\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{80\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$80 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{20.3\%}
\newcommand{\daCurrentMeanSecurityPerc}{$20.3 \pm 0.1\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{20\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$20 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.203}
\newcommand{\daCurrentVulnFree}{$0.203 \pm 0.001$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.124 \pm 0.0$}
\newcommand{\daCurrentUpdatednessNominal}{0.0532}
\newcommand{\daCurrentUpdatedness}{$0.0532 \pm 0.0$}
\newcommand{\daCurrentUpdatednessPercNominal}{5.32\%}
\newcommand{\daCurrentUpdatednessPerc}{$5.32 \pm 0.0\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{5.3\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$5.3 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{3.79}
\newcommand{\daCurrentSecurityScore}{$3.79 \pm 0.0$}
\newcommand{\daDailyParticipationNominal}{899}
\newcommand{\daDailyParticipation}{$899 \pm 245$}
\newcommand{\daNumFullVersions}{1\,270}
\newcommand{\daNumSigFullVersions}{95}

@@

\newcommand{\daNumSigOSVersions}{28}

@@

\newcommand{\daNumFullVersionUpdates}{4\,590}
\newcommand{\daNumOSVersionUpdates}{3\,900}
\newcommand{\daUpdatesPerYearNominal}{1.26}
\newcommand{\daUpdatesPerYear}{$1.26 \pm 0.01$}

@@

\newcommand{\daNumFullOnlyVersionUpdates}{677}
\newcommand{\daNumSecurityUpdates}{1\,250}
\newcommand{\daNumPossibleSecurityUpdates}{2\,300}
\newcommand{\daOSCurveFitParamFirst}{84.4}
\newcommand{\daOSCurveFitParamSecond}{\num{0.00285}}
\newcommand{\daOSCurveFitRMSE}{0.115}
\newcommand{\daOSCurvePolyRMSE}{0.115}
\newcommand{\daOSCurveSplineRMSE}{0.115}
\newcommand{\daOSCurveHalfDeployedYearsNominal}{0.897}
\newcommand{\daOSCurveHalfDeployedYears}{$0.897 \pm 0.252$}
\newcommand{\daOSCurveHalfDeployedNominal}{327}
\newcommand{\daOSCurveHalfDeployed}{$327 \pm 91$}
\newcommand{\daOSCurveFullDeployedYearsNominal}{3.11}
\newcommand{\daOSCurveFullDeployedYears}{$3.11 \pm 71$}
\newcommand{\daOSCurveFullDeployedNominal}{1\,130}
\newcommand{\daOSCurveFullDeployed}{$1\,130 \pm 260\,000$}
\newcommand{\daAPICurveFitParamFirst}{99.7}
\newcommand{\daAPICurveFitParamSecond}{\num{0.00285}}
\newcommand{\daAPICurveFitRMSE}{0.112}
\newcommand{\daAPICurvePolyRMSE}{0.112}
\newcommand{\daAPICurveSplineRMSE}{0.112}
\newcommand{\daAPICurveHalfDeployedYearsNominal}{0.939}
\newcommand{\daAPICurveHalfDeployedYears}{$0.939 \pm 0.244$}
\newcommand{\daAPICurveHalfDeployedNominal}{343}
\newcommand{\daAPICurveHalfDeployed}{$343 \pm 89$}
\newcommand{\daAPICurveFullDeployedYearsNominal}{3.15}
\newcommand{\daAPICurveFullDeployedYears}{$3.15 \pm 71$}
\newcommand{\daAPICurveFullDeployedNominal}{1\,150}
\newcommand{\daAPICurveFullDeployed}{$1\,150 \pm 260\,000$}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.22 \pm 0.00$ & $0.33 \pm 0.00$ & $0.62 \pm 0.01$ & $3.97 \pm 0.02$ \\  Motorola & $0.18 \pm 0.00$ & $0.12 \pm 0.00$ & $0.72 \pm 0.02$ & $3.07 \pm 0.02$ \\  Samsung & $0.13 \pm 0.00$ & $0.04 \pm 0.00$ & $0.61 \pm 0.00$ & $2.75 \pm 0.00$ \\  Sony & $0.14 \pm 0.00$ & $0.19 \pm 0.00$ & $1.09 \pm 0.02$ & $2.63 \pm 0.02$ \\  HTC & $0.14 \pm 0.00$ & $0.10 \pm 0.00$ & $0.87 \pm 0.01$ & $2.63 \pm 0.02$ \\  asus & $0.20 \pm 0.00$ & $0.51 \pm 0.01$ & $6.01 \pm 0.07$ & $2.35 \pm 0.02$ \\  other & $0.06 \pm 0.00$ & $0.05 \pm 0.00$ & $1.04 \pm 0.01$ & $1.97 \pm 0.02$ \\  alps & $0.03 \pm 0.00$ & $0.19 \pm 0.01$ & $3.99 \pm 0.08$ & $0.80 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $5.00 \pm 0.05$ & $0.30 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.09 \pm 0.00$ & $6.00 \pm 0.08$ & $0.27 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table*}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{3.97}
\newcommand{\daSecScoreBestmanufacturerScore}{$3.97 \pm 0.0$}
\newcommand{\daSecScoreBestmanufacturerNumFullVersions}{135}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.272}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.272 \pm 0.007$}
\newcommand{\daSecScoreWorstmanufacturerNumFullVersions}{21}
\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.50 \pm 0.00$ & $0.54 \pm 0.01$ & $1.53 \pm 0.04$ & $4.71 \pm 0.04$ \\  Nexus 4 & $0.30 \pm 0.00$ & $0.82 \pm 0.01$ & $6.06 \pm 0.09$ & $3.69 \pm 0.04$ \\  Nexus 7 & $0.26 \pm 0.00$ & $0.74 \pm 0.01$ & $5.92 \pm 0.09$ & $3.24 \pm 0.04$ \\  other & $0.10 \pm 0.00$ & $0.14 \pm 0.00$ & $0.53 \pm 0.00$ & $3.03 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & $0.38 \pm 0.02$ & $2.91 \pm 0.04$ \\  HTC Sensation & $0.35 \pm 0.00$ & $0.01 \pm 0.01$ & $1.57 \pm 0.05$ & $2.44 \pm 0.05$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & $1.23 \pm 0.02$ & $2.28 \pm 0.02$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.06$ & $1.74 \pm 0.07$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $2.52 \pm 0.05$ & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $1.79 \pm 0.06$ & $0.90 \pm 0.05$ \\  GT-I9300 & $0.13 \pm 0.00$ & $0.01 \pm 0.00$ & $6.23 \pm 0.04$ & $0.58 \pm 0.01$ \\  GT-I9505 & $0.03 \pm 0.00$ & $0.13 \pm 0.00$ & $6.82 \pm 0.07$ & $0.52 \pm 0.01$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $3.03 \pm 0.05$ & $0.28 \pm 0.03$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & $6.93 \pm 0.08$ & $0.24 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $11.00 \pm 0.12$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}

@@

\newcommand{\daSecScoreBestmodelScoreNominal}{4.71}
\newcommand{\daSecScoreBestmodelScore}{$4.71 \pm 0.0$}

@@

\newcommand{\daSecScoreWorstmodelScore}{$0.0001 \pm 0.0273$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline nexus & $0.39 \pm 0.00$ & $0.48 \pm 0.00$ & $0.56 \pm 0.01$ & $5.17 \pm 0.02$ \\  notnexus & $0.10 \pm 0.00$ & $0.02 \pm 0.00$ & $0.53 \pm 0.00$ & $2.70 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table*}}
\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.27 \pm 0.00$ & $0.12 \pm 0.00$ & $0.37 \pm 0.02$ & $3.87 \pm 0.03$ \\  T-Mobile & $0.22 \pm 0.00$ & $0.18 \pm 0.00$ & $0.40 \pm 0.01$ & $3.81 \pm 0.02$ \\  Orange & $0.22 \pm 0.00$ & $0.10 \pm 0.00$ & $0.36 \pm 0.02$ & $3.64 \pm 0.04$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & $0.43 \pm 0.02$ & $3.42 \pm 0.03$ \\  3 & $0.20 \pm 0.00$ & $0.09 \pm 0.00$ & $0.47 \pm 0.02$ & $3.38 \pm 0.03$ \\  Vodafone uk & $0.14 \pm 0.00$ & $0.13 \pm 0.00$ & $0.52 \pm 0.03$ & $3.17 \pm 0.04$ \\  AT\&T & $0.14 \pm 0.00$ & $0.08 \pm 0.00$ & $0.43 \pm 0.02$ & $3.13 \pm 0.02$ \\  unknown & $0.11 \pm 0.00$ & $0.20 \pm 0.00$ & $0.84 \pm 0.01$ & $2.88 \pm 0.02$ \\  Verizon & $0.19 \pm 0.00$ & $0.09 \pm 0.00$ & $0.82 \pm 0.02$ & $2.84 \pm 0.02$ \\  n Telenor & $0.04 \pm 0.00$ & $0.12 \pm 0.00$ & $1.21 \pm 0.02$ & $1.89 \pm 0.02$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & $1.47 \pm 0.03$ & $1.41 \pm 0.03$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $1.88 \pm 0.02$ & $0.93 \pm 0.01$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $2.07 \pm 0.04$ & $0.91 \pm 0.03$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.55 \pm 0.04$ & $0.55 \pm 0.02$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}

@@

\newcommand{\daSecScoreBestoperatorScoreNominal}{3.87}
\newcommand{\daSecScoreBestoperatorScore}{$3.87 \pm 0.0$}
\newcommand{\daSecScoreBestoperatorNumFullVersions}{100}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.548}
\newcommand{\daSecScoreWorstoperatorScore}{$0.548 \pm 0.018$}

@@

\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline equal & 0.0 & 0.0667 & 0.0 & 0.0 \\weight $m$ & 0.2 & 0.4 & 0.0714 & 0.0 \\$f$ & 0.4 & 0.733 & 0.5 & 0.0 \\weight $u$ & 0.4 & 0.0667 & 0.143 & 0.0 \\$m$ & 0.6 & 0.733 & 0.357 & 0.5 \\$u$ & 0.9 & 0.667 & 0.786 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline $m$ & $-1.67 \pm 2.25$ & $-0.66 \pm 2.54$ & $-3.3 \pm 1.3$ & $-3.4 \pm 1.8$ \\weight $m$ & $-0.264 \pm 0.276$ & $-0.0991 \pm 0.32$ & $-0.461 \pm 0.167$ & $-0.488 \pm 0.216$ \\equal & $-0.108 \pm 0.062$ & $-0.0368 \pm 0.112$ & $-0.146 \pm 0.045$ & $-0.165 \pm 0.033$ \\weight $u$ & $-0.0609 \pm 0.122$ & $-0.0113 \pm 0.232$ & $0.024 \pm 0.081$ & $-0.0061 \pm 0.12$ \\$u$ & $0.366 \pm 1.61$ & $0.219 \pm 2.12$ & $1.55 \pm 0.94$ & $1.42 \pm 1.48$ \\$f$ & $0.976 \pm 0.564$ & $0.331 \pm 1.01$ & $1.31 \pm 0.40$ & $1.48 \pm 0.29$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}
\newcommand{\daGPAPICurveFitParamFirst}{80.8}
\newcommand{\daGPAPICurveFitParamSecond}{\num{0.00258}}
\newcommand{\daGPAPICurveFitRMSE}{0.179}
\newcommand{\daGPAPICurvePolyRMSE}{0.178}
\newcommand{\daGPAPICurveSplineRMSE}{0.178}
\newcommand{\daGPAPICurveHalfDeployedYearsNominal}{0.957}
\newcommand{\daGPAPICurveHalfDeployedYears}{$0.957 \pm 0.469$}
\newcommand{\daGPAPICurveHalfDeployedNominal}{349}
\newcommand{\daGPAPICurveHalfDeployed}{$349 \pm 171$}
\newcommand{\daGPAPICurveFullDeployedYearsNominal}{3.4}
